???

### 2017-01-24 docs/language_constraint.tex
tweaks
Introduction V2; Sections 3-5 V1

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2017}
\usepackage{times}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage[normalem]{ulem}
\usepackage{url}

@@

\newcommand\BibTeX{B{\sc ib}\TeX}
\newcommand{\secref}[1]{Section~\ref{ssec:#1}}
\newcommand{\isection}[2]{\section{#1}\label{ssec:#2}}
\newcommand{\isectionb}[1]{\section{#1}\label{ssec:#1}}

\newcommand{\ms}[1]{{\color{cyan}\{\textit{#1}\}$_{ms}$}}
\newcommand{\roy}[1]{\footnote{\color{red}{\textbf{Roy: #1}}}}
\newcommand{\royb}[2]{{\color{red}{\sout{#1}}}{\color{green}{#2}}}
\newcommand{\royc}[3]{\royb{#1}{#2}\roy{#3}}

@@

\section{Introduction}
Writing style is defined as the choice of words, spelling, grammar and punctuation made by the author.\footnote{\url{https://en.wikipedia.org/wiki/Writing_style}}
It is often affected by inter-writer factors such as age \cite{Schler:2006}, gender \cite{Argamon:2003}, native language \cite{Koppel:2005}, or mere personality \cite{Stamatatos:2009}, but also by other parameters such as the sentiment of the text \cite{Davidov:2010} and whether it is sarcastic \cite{Tsur:2010}.  
In this paper we study to what extent is writing style affected by more intricate factors, such as the type of constraints put on the author.

As a testbed, we experiment with the story cloze task \cite{Mostafazadeh:2016}. 
This task was created by having authors write five-sentence self-contained stories.
Following, a subset of the the stories was given to another group of authors, who were shown only the first four sentences of each story, 
and were asked to write two one-sentence endings for it: a {\it correct} ending, and a {\it wrong} ending.
The goal of the task is to determine which of the endings is the correct one.

Interestingly, although originally intended to be a machine reading task, the compilation of this task raises several research questions which seem to differ from the original intent of the designers.
First, do authors use different style when asked to write a {\it correct} sentence, compared to a {\it wrong} sentence?
Second, do authors use different style when writing the ending as part of their own five sentence story, compared to reading four sentences, and then writing a standalone (correct) ending?

We show that the answer to both of these questions is positive. 
We train a linear classifier, using simple stylistic features, such as sentence length, character n-grams and PoS counts. 
We show that on a balanced dataset (random guess is 50\%) our classifier can distinguish between {\it correct} and {\it wrong} sentences in 64.5\% of the cases. 
Importantly, the classifier is trained {\bf only} on the last sentences, and does not consider the four input sentences.
It is also trained on a set of positive samples and a set of negative ones, rather than pairs of (positive, negative) pairs, as in the original story cloze task.
Furthermore, when trained to distinguish between original endings and new endings, the classifier obtains 70.9\% accuracy.

In order to estimate the quality of our results, we turn back to the story cloze task.
We show that using our classifier, we are able to obtain 71.6\% accuracy on the task, a 12\% improvement compared to the published state-of-the-art results \cite{Speer:2016}.\footnote{Recently, a shared task for the story cloze task has been published (\url{https://competitions.codalab.org/competitions/15333}). 
At the time of submission, the leading results is 71.1\%, which is much closer to our results, although still inferior.
No details about the methods used to generate this result are available.}

We present an ablation study which shows that the style differences are realized in syntactic features (such as the over/under use of coordination words like ``and'' and ``but'').
Furthermore, we also show that sentiment plays an important role in the writing style differences.
For instance, one of the key features for distinguishing between correct and wrong sentences is the over-representation of the word ``hate" by the latter.

Our results suggest that writing style is affected by the the writer's state of mind.
Writing a sentence intended to be {\it wrong} turns out quite differently than a sentence intended to be {\it correct}. 
Similarly, writing a sentence as part of the story is different from reading a story, and then writing the final sentence.
These differences can be distinguished to a large extent by simple machine learning tools.

The results presented here also provide valuable lessons for designing new NLP tasks.
Although \cite{Mostafazadeh:2016} seem to have put a lot of effort into designing the task, 
addressing many potential methodological flaws (see \secref{ROC_Story}), the importance of a few allegedly minor details were underestimated. 
%We show that these details are actually very significant.

Finally, we show that our stylistic features can benefit from combining with a machine-reading model, for which this task was designed.
We train an neural language model on the original five sentence training corpus, and then compute the language probability of each of the candidates answers. 
We add the numbers as features in our linear classifier, and get an additional 4\% improvement (75.6\%).

the reminder of this paper is organized as follows. In \secref{ROC_Story} we introduce the cloze story task.
We present our model, our experiments and our results at sections \ref{ssec:Model}, \ref{ssec:Experiments} and \ref{ssec:Results}, respectively.
Sections \ref{ssec:Ablation} and \ref{ssec:Discussion} present an ablation study and a discussion, while \secref{Related}  surveys related work. 
We conclude at \secref{Conclusion}.

@@

\subsection{Neural Language Model}
\ms{Below is a messy dump of all the hyper parameters... Didn't know how many details were needed}\roy{The level of description seems fine (we might remove some of them if space is an issue, but for now it's good. What I'm missing here are (a) an introductory 1-2  sentences to what are we doing here (I realize that it is not 100\% clear from the intro what is the role of these experiments other than showing that we have STOA results, so this can come later\\
(b) A one-sentence description of your model. Currently, there is no clear separation between the model (RNN using LSTM) and the technical details. 
Some general description of the model, and specifically the motivation behind (nothing fancy, just saying that we applied state-of-the-art LM tools, 
which resemble the tools the authors had in mind when they designed the task).}

@@

To construct features for the Story Cloze task, we scored each of the two endings using our neural language model. We computed the probability of each ending given the first four sentences $p_\theta(ending|story)$, as well as the probability of the endings out of context $p_\theta(ending)$. We also included the likelihood ratio $\frac{p_\theta(ending|story)}{p_\theta(ending)}$ into our classifier.\roy{This will probably change once we have the rest of the paper, but generally a few things that are missing:
(a) performance of the model as a standalone (both how we evaluated it and how much it got).
(b) modifying this paragraph to indicate that in order to combine between the style features presented in this paper and this model, we did the above.
(c) results of the combination (75.1\%).\\
These numbers might best fit in a small table.}
\isectionb{Experiments}

\isectionb{Results}

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2017}
\usepackage{times}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage[normalem]{ulem}
\usepackage{url}
\usepackage{pgfplots}
\usepackage{tikz}

% Define bar chart colors
%
\definecolor{bblue}{HTML}{4F81BD}
\definecolor{rred}{HTML}{C0504D}
\definecolor{ggreen}{HTML}{9BBB59}
\definecolor{ppurple}{HTML}{9F4C7C}

@@

\newcommand\BibTeX{B{\sc ib}\TeX}

% Writing macros
\newcommand{\secref}[1]{Section~\ref{ssec:#1}}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\newcommand{\tabref}[1]{Table~\ref{#1}}
\newcommand{\isection}[2]{\section{#1}\label{ssec:#2}}
\newcommand{\isectionb}[1]{\section{#1}\label{ssec:#1}}
\newcommand{\com}[1]{}

% Editing macros
\newcommand{\ms}[1]{{\color{cyan}\{\textit{#1}\}$_{ms}$}}
\newcommand{\roy}[1]{\footnote{\color{red}{\textbf{Roy: #1}}}}
\newcommand{\royb}[2]{{\color{red}{\sout{#1}}}{\color{green}{#2}}}
\newcommand{\royc}[3]{\royb{#1}{#2}\roy{#3}}
\renewcommand{\ms}[1]{}
\renewcommand{\roy}[1]{}
\renewcommand{\royb}[1]{}
\renewcommand{\royc}[1]{}

@@

\section{Introduction}
Writing style is defined as the the author's choice of words, spelling, grammar and punctuation.\footnote{\url{https://en.wikipedia.org/wiki/Writing_style}}
It is often affected by inter-writer factors such as age \cite{Schler:2006}, gender \cite{Argamon:2003}, native language \cite{Koppel:2005}, or mere personality \cite{Stamatatos:2009}, but also by other parameters such as the sentiment of the text \cite{Davidov:2010} and its level of sarcasm \cite{Tsur:2010}.  
In this paper we study to what extent is writing style affected by more intricate factors, such as the type of constraints put on the author.

As a testbed, we experiment with the story cloze task \cite{Mostafazadeh:2016}. 
In this task, authors were asked to write five-sentence self-contained stories.
Following, the stories were given to another group of authors, who were shown only the first four sentences of each story, 
and were asked to write two one-sentence endings for it: a {\it correct} ending, and a {\it wrong} ending.
The goal of the task is to determine which of the endings is the correct one.
\tabref{ROC-example} shows an example of an original story, a {\it correct} story and a {\it wrong} story.

\begin{table}[!t]
\small
\begin{tabular}{|p{.95cm}|p{6cm}|} \hline
{\bf Type} & {\bf Example} \\ \hline
{\it Original} story & My mother loves clocks that chime.	Her house is full of them.	She sets them each a little different so she can hear them chime.	It sounds like a bell tower during a wedding in her house all day.	{\color{blue}{When I visit I stop them or I'd never be able to sleep at night.}} \\ \hline
{\it Correct} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{green}{She felt buyer's remorse after the purchase.}} \\ \hline
{\it Wrong} story & I Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	Kathy hated buying shoes.	{\color{red}{Kathy hated buying shoes.}} \\ \hline
\end{tabular}
\caption{\label{ROC-example}}
Examples of stories from the story cloze task. The first row shows an original story written by one author. 
The second and third row show two endings of the same story: a {\it correct} ending and a {\it wrong} one.
%\end{center}
\end{table}

Interestingly, although originally intended to be a machine reading task, the compilation of this task raises several research questions which seem to differ from the original intent of the designers.
First, do authors use different style when asked to write a {\it correct} sentence, compared to a {\it wrong} sentence?
Second, do authors use different style when writing the ending as part of their own five sentence story, compared to reading four sentences, and then writing a standalone ({\it correct}) ending?

Our experiments indicate that the answer to both questions is positive. 
We train a linear classifier, using simple stylistic features, such as sentence length, character n-grams and PoS counts. 
First, we show that on a balanced dataset (random guess is 50\%) our classifier distinguishes between {\it correct} and {\it wrong} sentences in 64.5\% of the cases. 
Importantly, the classifier is trained {\bf only} on the last sentences, and does not consider the four input sentences.
%It is also trained on a set of positive samples and a set of negative ones, rather than pairs of (positive, negative) pairs, as in the original story cloze task.
Second, when trained to distinguish between original endings and new ({\it correct}) endings, the classifier obtains 70.9\% accuracy.

In order to estimate the quality of our results, we turn back to the story cloze task.
Using our classifier, we are able to obtain 71.5\% accuracy on the task, a 11.6\% improvement compared to the published state-of-the-art results \cite{Salle:2016}.\footnote{Recently, a shared task for the story cloze task has been published (\url{https://competitions.codalab.org/competitions/15333}). 
At the time of submission, the leading results is 71.1\%, which is much closer to our results, although still inferior.
No details about the methods used to generate this result are available.}
An ablation study shows that the style differences are realized in syntactic features (such as the over/under use of coordination words like ``and'' and ``but''),
but that sentiment also plays an important role in the writing style differences.
For instance, one of the key features for distinguishing between correct and wrong sentences is the over-representation of the word ``hate" in the latter.

\com{Our results suggest that writing style is affected by the the writer's state of mind.
Writing a sentence intended to be {\it wrong} turns out quite differently than a sentence intended to be {\it correct}. 
Similarly, writing a sentence as part of the story is different from reading a story, and then writing the final sentence.}

Our results may have a wide impact on a range of fields. 
First, they have the potential to shed light on cognitive processes that take place in the brain during writing.
Second, our results might have a more practical value in an era when fake news are becoming prominent,
as they suggest that these might have different style compared to real news.
Third, the results presented here also provide valuable lessons for designing new NLP tasks,
both in terms of the potential impact of even the smallest details, and the need to carefully run baseline models.
%Although \cite{Mostafazadeh:2016} seem to have put a lot of effort into designing the task, 
%addressing many potential methodological flaws (see \secref{ROC_Story}), the importance of a few allegedly minor details were underestimated. 
%We show that these details are actually very significant.

Finally, one interesting question that remains open is whether state-of-the-art machine reading tools, for which this task was designed, 
capture in fact the same stylistic features as our linear classifier. 
We show that this is not the case. 
We train a neural language model on the original five sentence training corpus, and then compute the language probability of each of the candidates answers. 
We add the numbers as features in our linear classifier, and get an additional 3.6\% improvement (75.1\%).

the reminder of this paper is organized as follows. In \secref{ROC_Story} we introduce the cloze story task.
We present our model and our experiments at sections \ref{ssec:Model} and \ref{ssec:Experiments} respectively.
Sections \ref{ssec:Ablation} and \ref{ssec:Discussion} present an ablation study and a discussion, while \secref{Related}  surveys related work. 
We conclude at \secref{Conclusion}.

@@

The goal of this paper is to determine to what extent does constraining authors in their writing assignments lead to them adopting different writing styles. 
In order to answer these questions, we use simple, classic NLP tools, which have been shown to be very effective for recognizing style (see \secref{Related}).
We describe our model below.

We train a linear SVM classifier to distinguish between different endings. 
Each feature vector is computed using the words in one ending, without considering earlier parts of the story. 
We use the following style features.

\begin{itemize}
\item{Length} The number of words in the sentence.
\item{Word n-grams} We use sequences of 1-5 words. Following \cite{Tsur:2010,Schwartz:2013}, we distinguish between high frequency and low frequency words. 
Specifically, we replace content words with their part-of-speech tags (Nouns, Verbs, Adjectives and Adverbs).
\item{Character n-grams} Character n-grams are one of the most useful features in identifying author style \cite{Stamatatos:2009}. 
We used character 5-grams.
\end{itemize}

\isectionb{Experiments}
We design two experiments to answer our research questions. 
The first is an attempt to distinguish between {\it correct} and {\it wrong} endings.
The second attempts to distinguish between original endings and new {\it correct} endings.
We describe both experiments below.

\paragraph{Experiment 1: Correct/Wrong Endings.}
The goal of this experiment is to measure to what extent  style features capture differences between {\it correct} and {\it wrong} endings.
As the cloze story task doesn't have a training corpus for the {\it correct} and {\it wrong} endings, we use the development set as our training set. 
We split it (90/10) into our training and development set. We keep the story cloze test set as is.
The final size of our training/development/test sizes are 3366/374/3742, respectively.

We take  {\it correct} endings as positive samples and {\it wrong} endings as our negative examples. 
By ignoring the coupling between {\it correct}/{\it wrong} pairs, we are able make a more general claim about the style used when writing each of the tasks.

We add a special START symbol at the beginning of each sentence. 
For computing our features, we keep n-gram (character or word) features that occur at least five times in the training set.\footnote{Virtually all sentences end with a period, so no need for an END token}
For the PoS features, we tag each sentence with the Spacy PoS tagger.\footnote{\url{spacy.io/}}
We use  sklearn's LinearSVC SVM implementation\footnote{\url{scikit-learn.org/stable/modules/generated/sklearn.svm.LinearSVC.html}} 
with L2 loss. We grid search the regularization parameter on our development set.

\paragraph{Experiment 2: Original/New Endings.}

Here the goal is to measure whether writing the ending as part of a story imposes different style compared to writing a ({\it correct}) ending to an existing story.
We use the endings of the original ROC stories as our {\it original} training samples and {\it correct} endings from the ROC stories development set as {\it new} training samples.
As there are far more {\it original} samples than {\it new} ones, we randomly select $N$ {\it original} samples, where $N$ is the number of {\it new} samples,
such that we have balanced labels in our training, validation and test sets.
We apply the same experimental decisions as in Experiment 1, and repeat this process 5 times while reporting the average.

\paragraph{Results.}
\figref{results} shows our results.
Results show that for Experiment 1, our model obtains results well above a random baseline -- 64.5\% classification accuracy. 
For Experiment 2, we get even higher results -- 70.9\%. 
These numbers indicate that these different writing tasks clearly impose a different writing style on authors.

As a complementary experiment, we measured whether these style differences are additive. 
That is, whether the style differences between {\it correct} endings and {\it wrong} ones are different from the differences between {\it correct} and {\it original} endings.
We repeated Experiment 2, this time comparing between {\it original} and {\it wrong} sentences. 
Our hypothesis is that differences would be even clearer. 
Our results (\figref{results}) show that this is indeed the case: the classifier's accuracy jumps to 78\%.

\begin{figure}
\begin{tikzpicture}
\small
    \begin{axis}[
        width  = 0.45*\textwidth,
        height = 4cm,
      %  major x tick style = transparent,
        ybar=2*\pgflinewidth,
       % bar width=14pt,
        ymajorgrids = true,
        ylabel = {Classification Performance},
        symbolic x coords={{\it Correct/Wrong}, {\it Original/New}, {\it Original/Wrong}},
        xtick = data,
        scaled y ticks = false,
        %enlarge x limits=0.25,
        ymin=0.4,
        legend cell align=left,
        legend style={
                at={(1,1.05)},
                anchor=south east,
                column sep=1ex
        }
    ]
        \addplot[style={bblue,fill=bblue,mark=none}]
            coordinates {({\it Correct/Wrong}, 0.5) ({\it Original/New}, 0.5) ({\it Original/Wrong},.5)};

        \addplot[style={rred,fill=rred,mark=none}]
            coordinates {({\it Correct/Wrong}, 0.645) ({\it Original/New}, 0.709) ({\it Original/Wrong},0.78)};

        \legend{Random Baseline, Our Model}
    \end{axis}
\end{tikzpicture}
\caption{\label{results} Results of  experiments 1 and 2 (left two charts). 
Rightmost experiment shows a control experiment which classifies {\it original} endings vs \textit{\textbf{wrong}} endings. }
\end{figure}

\paragraph{Story Cloze.}
Results of Experiment 1 indicate that {\it correct} and {\it wrong} endings are characterized by different styles.
In order to estimate the quality of our classification results, we tackle the story cloze task using our classifier.
This classification task is much more constrained than Experiment 1, as here the task is given two endings, which one is {\it correct} and which is {\it wrong}.
In order to solve the task, we use the output of our trained classifier. 
For each pair of endings $e_1,e_2$, if both endings have different classification labels, we keep these labels. 
If they share the same label, we use the classifier confidence level as a deciding factor: the label of the one with the lower confidence is reversed.

\tabref{cloze_results} shows our results on the story cloze test set. Our classifier obtains 71.5\% accuracy, which is 11.6\% better than the published state-of-the-art result on the task.
Importantly, unlike previous approaches, our classifier does not require the story corpus training data, and in fact doesn't even look at the first four sentences of the story in question.
These numbers indicate that the styles between {\it correct} and {\it wrong} are indeed very different.

Other than the published works that tackled this task, a few  recent works published their results in the LSDSem shared task website.\footnote{\url{https://competitions.codalab.org/competitions/15333}} 
As to the time of submission, our results are still state-of-the-art (though by a much smaller margin). No other information other than the name of the group and their results is available.

\begin{table}[!t]
\begin{center}
\small
\begin{tabular}{|c|c|} \hline
{\bf Model} & {\bf Results} \\ \hline
{DSSM} \cite{Mostafazadeh:2016} & 0.585 \\ \hline
{ LexVec} \cite{Salle:2016} & 0.599 \\ \hline
{RNN}		& 0.677 \\ \hline
{\bf Our Model} & {\bf 0.715} \\ \hline
{\bf Combined (Our model, RNN)} & {\bf 0.751} \\ \hline\hline
{ tbmihaylov (shared task)} & 0.711\\ \hline
{ Niko (shared task)}	& 0.7\\ \hline\hline
Human judgment & 1 \\ \hline
\end{tabular}
\end{center}
\caption{\label{cloze_results}}
Results on the test set of the cloze story task. 
Upper part are published results (Lexvec results are taken from \cite{Speer:2016}).
Bottom part are taken from the cloze task shared task webpage.
\end{table}

\paragraph{Most Discriminative Feature Types.}
A natural question that follows this study is which features are most helpful in making predictions about writing style. 
To answer this question, we re-ran Experiment 1 with different sub-groups of features. 
\tabref{subgroups} shows our results. Results clearly show that  character n-grams are the most effective style predictors, reaching within less than 2\% of the full model.
These findings are in line with previous works that used character n-grams along with other types of features to predict writing  style \cite{Schwartz:2013}.

\begin{table}[!t]
\begin{center}
\small
\begin{tabular}{|c|c|} \hline
{\bf Feature Type} & {\bf Result}\\ \hline
Word n-grams & 0.646 \\ \hline
Char n-grams & 0.699 \\ \hline
Word n-grams, length, char n-grams (Full Model) & 0.715 \\ \hline

\end{tabular}
\end{center}
\caption{\label{subgroups}}
Results on Experiment 1 with different types of features.
\end{table}

\paragraph{Most Salient Features.}
In order to understand which features were most salient, we repeated Experiment 1, this time running SVM with L1 norm, such that it generates a sparse separating hyperplane. 
This came at a minor cost of less than 2\% in performance compared to our L2 results (0.697 compared to 0.715).  
\tabref{features} shows the 5 features with the highest positive and negative weights in the hyperplane. 
These correspond to the 5 most salient features for {\it correct} and {\it wrong} endings, respectively.

The table shows a few interesting trends. 
First, some syntactic features play become salient when authors are asked to write {\it wrong} vs. {\it correct} endings.
For instance, {\it correct} endings are more likely to the coordinator ``but'', while {\it wrong} ones would prefer to use ``and''.

More interestingly, {\it correct} endings are likely to use positive words (e.g., `` bett'', which in all cases stands for `` bett{\bf er}''), while  {\it wrong} endings would use negative words (e.g., `` hate''). 
The idea that  sentiment would play a role in this task was suggested in the original story cloze paper, where two sentiment-based baselines were evaluated. 
However, these baselines measured the relative sentiment between the ending and the previous sentences, and did not test whether there is a general tendency of the {\it wrong} endings to have a negative sentiment, and the {\it correct} one to have a positive sentiment.
Indeed, the performance of both these baselines was roughly chance-level.

\begin{table}[!t]
\begin{center}
\small
\begin{tabular}{|c|c|} \hline
{\bf Positive} & {\bf Negative}\\ \hline
` time' & `ed of'\\ \hline
` bett' & `and d'\\ \hline
`found' & `threw'\\ \hline
`but' & `ever '\\ \hline
`ally ' & ` hate'\\ \hline

\end{tabular}
\end{center}
\caption{\label{features}}
The top 5 most discriminative features for predicting {\it correct} (Positive)  and {\it wrong} (Negative) endings.\end{table}

\paragraph{Neural Language Model.}
\ms{Below is a messy dump of all the hyper parameters... Didn't know how many details were needed}\roy{The level of description seems fine (we might remove some of them if space is an issue, but for now it's good. What I'm missing here are (a) an introductory 1-2  sentences to what are we doing here (I realize that it is not 100\% clear from the intro what is the role of these experiments other than showing that we have STOA results, so this can come later\\
(b) A one-sentence description of your model. Currently, there is no clear separation between the model (RNN using LSTM) and the technical details. 
Some general description of the model, and specifically the motivation behind (nothing fancy, just saying that we applied state-of-the-art LM tools, 
which resemble the tools the authors had in mind when they designed the task).}

@@

To construct features for the Story Cloze task, we scored each of the two endings using our neural language model. We computed the probability of each ending given the first four sentences $p_\theta(ending|story)$, as well as the probability of the endings out of context $p_\theta(ending)$. We also included the likelihood ratio $\frac{p_\theta(ending|story)}{p_\theta(ending)}$ into our classifier.\roy{This will probably change once we have the rest of the paper, but generally a few things that are missing:
(a) performance of the model as a standalone (both how we evaluated it and how much it got).
(b) modifying this paragraph to indicate that in order to combine between the style features presented in this paper and this model, we did the above.
(c) results of the combination (75.1\%).\\
These numbers might best fit in a small table.}
